### 2019-11-27 paper/paper.tex
typo

These pre-trained models are usually trained on the ImageNet dataset\cite{imagenet_cvpr09}. This dataset is a large
collection of images of real world objects such as animals, like dogs and cats, and other objects like cars.
Thus we would expect these models to be good at extracting features from images that are similar to ImageNet,
aka realworld, everyday objects. If we want to apply these models to images that are very different from 
the ImageNet dataset, such as the Human Protein dataset, we would expect the model to 
not be able to extract very good features.

@@

Researches in the biology field have been made a lot easier by data analysis nowadays. Training machines for tedious work is saving experts a lot of time and also makes it possible to learn a mass of variations thoroughly. Specifically for protein study, an application is classifying well-known proteins, which is essential for learning a novel protein based on the group to which it is predicted to belong\cite{subcellular}.

@@

The ResNet50V2 model is conveniently structured as distinct residual blocks.
For our experiments we picked the outputs of 4 different residual blocks, evenly spaced between each other, in the model
as our final feature map. The output of the chosen hidden layers is a large amount of 
feature maps. Due to limitations of our compute resources, we chose not to directly flatten the feature maps and connect it to a dense prediction
layer due to the amount of feature maps ResNet50V2 outputs and thus the amount of parameters that would need. We chose to reduce the number of 
feature maps from the output by first passing it through a 1x1 convolution layer\cite{szegedy2014going} with 
relu activation. This allows us to reduce the number of final feature maps in a efficient way, significantly reducing the number of parameters and training time. 
We then flatten the feature maps using global average pooling\cite{Lin2013NetworkIN}, and then connect to a 
fully connected dense layer for prediction.

>>>>

These pre-trained models are usually trained on the ImageNet dataset\cite{imagenet_cvpr09}. This dataset is a large
collection of images of real world objects such as animals, like dogs and cats, and other objects like cars.
Thus we would expect these models to be good at extracting features from images that are similar to ImageNet,
aka real world, everyday objects. If we want to apply these models to images that are very different from 
the ImageNet dataset, such as the Human Protein dataset, we would expect the model to 
not be able to extract very good features.

@@

Researches in the biology field have been made a lot easier by applying data analysis nowadays. Training machines for tedious work is saving experts a lot of time and also makes it possible to learn a mass of variations thoroughly. Specifically for protein study, an application is classifying well-known proteins, which is essential for learning a novel protein based on the group to which it is predicted to belong\cite{subcellular}.

@@

The ResNet50V2 model is conveniently structured as distinct residual blocks.
For our experiments we picked the outputs of 4 different residual blocks, evenly spaced between each other, in the model
as our final feature map. The output of the chosen hidden layers is a large amount of 
feature maps. Due to limitations of our compute resources, we chose not to directly flatten the feature maps and connect it to a dense prediction
layer due to the amount of feature maps ResNet50V2 outputs and thus the amount of parameters that would need. We chose to reduce the number of 
feature maps from the output by first passing it through a 1x1 convolution layer\cite{szegedy2014going} with 
Relu activation. This allows us to reduce the number of final feature maps in an efficient way, significantly reducing the number of parameters and training time. We then flatten the feature maps using global average pooling\cite{Lin2013NetworkIN}, and then connect to a 
fully connected dense layer for prediction.
